COG-ED Manuscript

### 2022-01-17 06_Paper/COG-ED/Manuscript.Rmd
tried implementing pdf-import for design table

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
wordcount         : "X"
bibliography      : CERED.bib
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
editor_options: 
  markdown: 
    wrap: sentence
---

@@

  # save plot
  Figure3 <- h2c_jn$plot

@@

  sca_plot <- ggarrange(sca_upperplot, sca_lowerplot, nrow = 2, heights = c(1,2.5))

@@

We collected data from $N = 15$ participants.
One participant's NASA-TLX data is incomplete due to a technical error, so hypotheses 1c and 3b are analyzed using the 14 complete data sets.
The results showed increases in subjective and objective task load measures with higher n-back level.
Importantly, SVs were lower for higher n-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
The MLM revealed that n-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers.
And finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the AUC of NASA-TLX scores did.
All results are detailed in the *Supplementary Material*.

@@

# Figure Captions

*Fig.1* Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.

*Fig.2* Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation.

@@

@@

`r Figure2`
*Fig.2* Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation.

@@

>>>>

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
wordcount         : "X"
bibliography      : CERED.bib
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage{pdfpages}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

  # save plot
  h2c_jn.plot <- h2c_jn$plot

@@

  Figure3 <- ggarrange(sca_upperplot, sca_lowerplot, nrow = 2, heights = c(1,2.5))

@@

We collected data from $N = 15$ participants.
One participant's NASA-TLX data is incomplete due to a technical error, so hypotheses 1c and 3b are analyzed using the 14 complete data sets.
The results showed increases in subjective and objective task load measures with higher n-back level.
Importantly, SVs were lower for higher n-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
The MLM revealed that n-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not.
The specification curve analysis showed that this pattern was true for all 63 pipelines.
And finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the AUC of NASA-TLX scores did.
All results are detailed in the *Supplementary Material*.

@@

# Figures and figure Captions

```{r figure1, echo=FALSE, message=FALSE, warning=FALSE}

  include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))

```
*Fig.1* Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.

`r Figure2`
*Supplementary Figure 1* Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation.

`r Figure3`
*Supplementary Figure 2* Results of the specification curve analysis for the multi level model. The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values. Estimates with $p<.01$ are indicated by a dot on the line. The lower panel shows the preprocessing steps of each corresponding pipeline. The $BF10$ of each pipeline's multi level model approached infinity.

@@

\includepdf[pages={-}]{here("02_Hypotheses", "Design_Table_T1.pdf")}

@@

`r Figure2`
*Supplementary Figure 1* Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation.

@@

Specification curve analysis:

`r Figure3`
*Supplementary Figure 2* Results of the specification curve analysis for the multi level model. The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values. Estimates with $p<.01$ are indicated by a dot on the line. The lower panel shows the preprocessing steps of each corresponding pipeline. The $BF10$ of each pipeline's multi level model approached infinity.
